---
title: "Careers Output Doc"
author: "Jeff Kennedy"
date: "23 January 2018"
output:
  html_document:
    keep_md: yes
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries, include=FALSE}
library(skimr)
library(tidyverse)
library(kableExtra) # For formatting tables via Kable
library(sjPlot)
library(psych)
library(lubridate)
library(haven)
library(here)
library(glue)
library(stringr)
library(readxl)
library(sjmisc)
library(foreign)
library(lme4)
library(lavaan)
library(car)
load("../data/responses.Rdata")
source("../munge/01-munge.R")
source("../munge/02-munge missing vals analysis.R")
source("../munge/03-munge create scale scores.R")
# knitr::knit_exit() for use in debugging, can move to different place in doc
```
### Descriptives for Career Facilitator Scales

#### Cronbach alpha and number of items for 7-point scales:
```{r, echo = FALSE}
alpha_7 <- round(scores_7$alpha[,-1], 2)
# colnames(alpha_7)[colnames(alpha_7)=="scores_7$alpha[, -1]"] <- "alpha"
# sjt.df(alpha_7, 
#        describe = FALSE, 
#        title = "Alpha for 7-point Scales", 
#        altr.row.col=FALSE,
#        hide.progress = TRUE)
n_items_7 <- round(scores_7$n.items[-1], digits = 2)
# colnames(n_items_7)[colnames(alpha_7)=="scores_7$n.items[-1]"] <- "n_items"
# sjt.df(n_items_7, 
#        describe = FALSE, 
#        title = "Number of items in 7-point Scales", 
#        altr.row.col=FALSE,
#        hide.progress = TRUE)
ScaleNames7 <- dimnames(scores_7$alpha)[[2]][-1]
tibble(ScaleNames7, alpha_7, n_items_7) %>% 
    kable("html") %>% 
    kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```
#### Cronbach alpha and number of items for 5-point scales:
```{r, echo = FALSE, results = 'asis'}
alpha_vals <- round(scores_5$alpha[,-1], digits = 2)
N_items <- scores_5$n.items[-1]
ScaleNames5 <- dimnames(scores_5$alpha)[[2]][-1]
tibble(ScaleNames5, alpha_vals, N_items) %>% 
    kable("html") %>% 
    kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)

```

#### CFA chi-sq and fit values for scales:
```{r CFA5, results = 'asis', echo = FALSE, warning = FALSE, message=FALSE}
cfanames5 <- map(names(keys.list_5[-1]), .f = ~ str_split(.x, "_")[[1]][2])
# Creates the model syntax
modelstmts5 <- glue('{cfanames5} =~ {map(keys.list_5[-1], .f = ~ 
                   collapse(.x, sep = " + "))}')
# Next step - get fit objects for each model
fitoutput5 <- map(modelstmts5, .f = ~ cfa(.x, data = responses))

# Put everything in a tibble
lm.output5 <- tibble(name = cfanames5,
                    model = modelstmts5,
                    fit = fitoutput5)

lm.output5 <- lm.output5 %>% 
    mutate(chisq = map_dbl(fit, ~ fitMeasures(.x, "chisq"))) %>% 
    mutate(df = map_dbl(fit, ~ fitMeasures(.x, "df"))) %>% 
    mutate(ntotal = map_dbl(fit, ~ fitMeasures(.x, "ntotal"))) %>%
    mutate(cfi = map_dbl(fit, ~ fitMeasures(.x, "cfi"))) %>% 
    mutate(tli = map_dbl(fit, ~ fitMeasures(.x, "tli"))) %>%
    mutate(rmsea = map_dbl(fit, ~ fitMeasures(.x, "rmsea"))) %>% 
    mutate(srmr = map_dbl(fit, ~ fitMeasures(.x, "srmr")))

lm.output5 %>% 
    select(-one_of(c("model", "fit"))) %>% 
    kable("html", digits = 3, 
          caption = "CFA fit for scales using 5-point rating scale") %>% 
    kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```


```{r CFA7, results = 'asis', echo = FALSE, warning = FALSE, message=FALSE}
cfanames7 <- map(names(keys.list_7[-1]), .f = ~ str_split(.x, "_")[[1]][2])
# Creates the model syntax
modelstmts7 <- glue('{cfanames7} =~ {map(keys.list_7[-1], .f = ~ 
                   collapse(.x, sep = " + "))}')
# Next step - get fit objects for each model
fitoutput7 <- map(modelstmts7, .f = ~ cfa(.x, data = responses))

# Put everything in a tibble
lm.output7 <- tibble(name = cfanames7,
                    model = modelstmts7,
                    fit = fitoutput7)

lm.output7 <- lm.output7 %>% 
    mutate(chisq = map_dbl(fit, ~ fitMeasures(.x, "chisq"))) %>% 
    mutate(df = map_dbl(fit, ~ fitMeasures(.x, "df"))) %>%
    mutate(ntotal = map_dbl(fit, ~ fitMeasures(.x, "ntotal"))) %>%
    mutate(cfi = map_dbl(fit, ~ fitMeasures(.x, "cfi"))) %>% 
    mutate(tli = map_dbl(fit, ~ fitMeasures(.x, "tli"))) %>%
    mutate(rmsea = map_dbl(fit, ~ fitMeasures(.x, "rmsea"))) %>% 
    mutate(srmr = map_dbl(fit, ~ fitMeasures(.x, "srmr")))

lm.output7 %>% 
    select(-one_of(c("model", "fit"))) %>% 
    kable("html", digits = 3, 
          caption = "CFA fit for scales using 7-point rating scale") %>% 
    kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```

#### Summary stats for demog vars
```{r, results = 'asis'}
skim(responses, Age, Seniority, Educ, TotSal, WkHours, TotDeps) %>% 
    kable()
```



The following tables use pairs.panels (first fig) and corPlot from psych package.

```{r correlation_plots, echo = FALSE}
splom.scales <- responses %>% 
    select(one_of(c("C5_CarAdv", "E4_CarMgt", "E5_DevAsst", "F2_MngCar", "F5_DevAss", 
                    "F6_ProcJust", "F7_DistJust", "F12_CareerSat", "F14a_CarSucc")))


pairs.panels(splom.scales)
corPlot(splom.scales, main = "Correlations of Main Scales", pval = FALSE, 
        numbers = TRUE)
```

The package skimr provides tidy one-line summaries of response frequencies.


